\documentclass[11pt]{letter}

\setlength{\textwidth}     {16.0cm}
\setlength{\textheight}    {30.5cm}
\setlength{\evensidemargin}{-0.5cm}
\setlength{\oddsidemargin} {-0.5cm}
\setlength{\topmargin}     {-4.0cm}
\setlength{\baselineskip}  { 0.5cm}

\address{Department of Computer Science,  \\
         Institute of Mathematics and Statistics, \\
         University of S\~ao Paulo \\ S\~ao Paulo, Brazil}
\signature{Prof. Ernesto G. Birgin \\
           egbirgin@ime.usp.br}

\date{July 22th, 2020}

\begin{document}

\begin{letter}{Professors Marco L\"ubbecke and Panos M. Pardalos\\
               Editors-in-Chief  \\
               Operations Research Forum}

\opening{Dear Professors Marco and Panos,}

\vspace{0.5cm}

We would like to submit our paper entitled ``Relax-and-fix heuristics
applied to a real-world lot-sizing and scheduling problem in the
personal care consumer goods industry'' by K. A. G. Araujo,
E. G. Birgin, M. S. Kawamura, and D. P. Ronconi for a possible
publication in Operations Research Forum.

In this paper we describe the application of the relax-and-fix
technique to a real-world problem that integrates lot sizing and
scheduling in the personal care consumer goods industry. The results
show that the technique worked very well, largely improving the
solutions adopted by the company. In addition, we describe the
instances in detail and make them available, so that all the results
can be reproduced and the instances can be used in future work to test
and compare new methods.

We confirm that this manuscript has not been published elsewhere and
is not under consideration by another journal. All authors have
approved the manuscript and agree with its submission.

We are confident this work fits Operations Research Forum's aim and
scope, and we believe that our findings would appeal to the readership
of the journal. We hope that you will find the paper interesting and
suitable for submission to Operations Research Forum.


\closing{Sincerely,}
\end{letter}
\end{document}


